Human Factors Influencing Visual Statistical Inference

### 2013-07-23 sociology_paper.tex
some typos

\usepackage{color}
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\dc}[1]{{\color{green} #1}}

@@

\begin{enumerate} \leftmargin 5cm  \itemsep 0in
\item Age group, with categories set to be 18-25, 26-30, 31-35, 36-40, 41-45, 46-50, 51-55, 56-60, above 60.
\item Gender, male of female.
\item Education level, with levels being high school or less, some under grad course, under graduate degree, some graduate courses, and graduate degree.
\item Geographical location, collected from the IP address of the participants' computer, as latitude, longitude, city and country. 
\end{enumerate}

@@

(*** No results are given for this model, are they????)

@@

*** Doesn't this need to go in a place so that it is obvious that all models described are fit with these routines, at the end of the section perhaps?? To fit all these mixed effect models the function $lmer()$ is used from R package $lme4$ by \cite{lme4:2011}. To obtain the $p$-values of fixed effect parameters estimates, normal approximation is used for $Z$ scores computed as the ratio of estimates to the estimated standard errors.

*** These models treat attempt as a linear effect, so that only linear increase or decrease is modelled *** something like this.

*** Also, you need to say something about examining the residuals, which is what is done in several of the parts of the results section.

>>>>

\usepackage{color}
\newcommand{\hh}[1]{{\color{magenta} #1}}
\newcommand{\dc}[1]{{\color{green} #1}}
\newcommand{\mm}[1]{{\color{blue} #1}}

@@

\begin{enumerate} \leftmargin 5cm  \itemsep 0in
\item Age group, with categories set to be 18-25, 26-30, 31-35, 36-40, 41-45, 46-50, 51-55, 56-60, above 60.
\item Gender, male or female.
\item Education level, with levels being high school or less, some under grad course, under graduate degree, some graduate courses, and graduate degree.
\item Geographical location, collected from the IP address of the participants' computer, as latitude, longitude, city and country. 
\end{enumerate}

@@

(\dc{*** No results are given for this model, are they????}  \mm{results are given in table \ref{tbl:model_result_demographics}})

@@

\dc{*** Doesn't this need to go in a place so that it is obvious that all models described are fit with these routines, at the end of the section perhaps??} To fit all these mixed effect models the function $lmer()$ is used from R package $lme4$ by \cite{lme4:2011}. To obtain the $p$-values of fixed effect parameters estimates, normal approximation is used for $Z$ scores computed as the ratio of estimates to the estimated standard errors. 
\dc{
*** These models treat attempt as a linear effect, so that only linear increase or decrease is modelled *** something like this.

*** Also, you need to say something about examining the residuals, which is what is done in several of the parts of the results section.}
